\documentclass[../main.tex]{subfiles}

\begin{document}

\subsection*{TEALS Technology Education And Literacy In Schools}
     Wisconsin Regional Manager, Madison, WI - 2017--present
	\begin{itemize}
		\item{Recruit, train, and support tech industry volunteers to team-teach high school CS classes.}
		\item{Train and support classroom teachers as they learn computer science content.}
		\item{Organize student outreach and enrichment opportunities, including internships and field trips.}
		\item{Build regional communities of practice around computer science education through events, trainings, social media, and resource curation.}
	\end{itemize}

\subsection*{Games + Learning + Society }
     Conference Co-Chair, Madison, WI - 2015--2016
	\begin{itemize}
		\item{Recruited and supervised other conference staff.}
		\item{Recruited conference speakers.}
		\item{Managed the conference web site and conference registration.}
		\item{Created and nanaged a six-figure budget.}
		\item{Found a suitable venue and determined catering needs for 500+ attendees.}
	\end{itemize}

\subsection*{Instructional Technology and Communication Assistant}
     DoIT Academic Technology, University of Wisconsin at Madison, Madison, WI - 2013--2015
	\begin{itemize}
		\item{Provided technical assistance and training to faculty and staff in Moodle and Desire to Learn.}
		\item{Assist faculty in using technology in instructional design.}
		\item{Developed in JavaScript, CSS and HTML for ARIS and SIFTR.}
		\item{Supported faculty and staff with academic technology issues.}
		\item{Provided technical support and forum moderation for MOOC with over 40,000 users.}
		\item{Designed games and new user trainings for ARIS.}
		\item{Resolved technical issues for users of Case Scenario/Critical Reader digital narrative tool.}
	\end{itemize}

\subsection*{Director of Religious Education}
     James Reeb Unitarian Universalist Congregation, Madison, WI - 2011--2014
	\begin{itemize}
		\item{Recruited, trained, and supervised over 20 volunteer teachers each semester.}
		\item{Coordinated inspiring and meaningful curriculum activities across 5 classrooms (ages 0--18).}
		\item{Organized community building workshops, fairs and events.}
		\item{Created and maintained digital pedagogy support and communication tools.}
	\end{itemize}

\subsection*{Technical Support Coordinator}
     United Cerebral Palsy of Greater Dane County, Madison, WI - 2012--2013
	\begin{itemize}
		\item{Administered Windows Server 2008, Exchange 2010, anti-virus, security, and backup systems.}
		\item{Provided technical support and training for over 65 Windows and iPad users.}
		\item{Developed organization-wide technology strategy to take advantage of new digital tools.}
	\end{itemize}

\subsection*{Information Support Specialist}
     McQuay International, Minneapolis, MN - 2005--2006
	\begin{itemize}
		\item{Programmed in FoxPro to improve and support a legacy order entry system processing over 1 million dollars in orders a day.}
		\item{Provided phone and email based training and troubleshooting for international sales reps and engineers.}
		\item{Created a new documentation database with tutorial documents for three major systems.}
	\end{itemize}

\subsection*{Programmer, Web Developer and System Administrator}
     Center for Demography in Health and Aging, Madison, WI - 2002--2005
	\begin{itemize}
		\item{Administered the OLDR (Off-line Longitudinal Data Repository) Red Hat Linux system.}
		\item{Developed CDHA's website using HTML, CSS, DreamWeaver and Photoshop.}
		\item{Designed PHP forms with dynamically linked ASP and SQL databases. }
		\item{Wrote extensive documentation for the IT systems and protocols.}
	\end{itemize}

\end{document}
