\documentclass[../main.tex]{subfiles}

\begin{document}

%todo Conference Reviews
%todo Bodgery

\subsection*{Board Member}
     Danenet - 2017 -- ongoing
\begin{itemize}
		\item{Advise on technology initiatives}
\end{itemize}

\subsection*{Director}
     MadHacks - 2016 -- 2017
\begin{itemize}
		\item{Leads student hackathon group which organizes technology events for 100-600 students. https://www.madhacks.org/}
	\end{itemize}

\subsection*{Chair of Education Committee}
     Bodgery Makerspace - 2016 -- ongoing
\begin{itemize}
		\item{Recruits local technology experts and artists to run workshops. Facilitates and supports educational outreach efforts. In addition, has taught classes in e-textiles, software licenses and privacy.}
	\end{itemize}

\subsection*{Electronic Textiles Volunteer Instructor}
     Madison Children's Museum - 2015
\begin{itemize}
		\item{Designed, Coordinated and Taught a workshop on electronic textiles for middle school girls. http://madisonchildrensmuseum.org/event/digi-design/}
	\end{itemize}

\subsection*{Saturday Science presenter}
     Wisconsin Institute for Discovery - 2016
\begin{itemize}
		\item{For this event, I designed and presented a hands-on e-textile table. Several electronic textile projects were created to be hands-on circuitry and programming concept demonstrations. Participants were also invited to try programming a LilyPad Arduino Proto-Snap development board which had been set up with example code and tutorial packets. 'Try it at home' handouts were also created.}
	\end{itemize}

\subsection*{Game Design and Code Club volunteer}
     Wingra School - 2015--2016
\begin{itemize}
		\item{Guide elementary school students in creating games with Scratch, Scratch Jr., Game Star Mechanic, and Google Sketchup in a weekly Game Design and Code after school club.}
	\end{itemize}

\subsection*{Tech Presenter}
     Expanding Your Horizons - 2015 \& 2016
\begin{itemize}
		\item{Worked with UW Professor Deb Deppeler to design a 1 hour 'Introduction to C Programming with E-Textiles' program for middle school girls. Final product included 4 sets of code with tutorial packets for the girls to explore different aspects of circuits, electronics and C programming, which are available under Creative Commons license}
	\end{itemize}


\subsection*{Hour of Code Volunteer}
     We Think Big, Inc. - 2015
\begin{itemize}
		\item{Helped local teachers explore computer programming at an Hour of Code event.}
	\end{itemize}

\subsection*{Wisconsin Science Festival Outreach Volunteer}{
UW Madison WACM (Women of Association for Computing Machinery)}{2015}{}
\begin{itemize}
		\item{Taught the basics of binary numbers to children and parent attendees of the Wisconsin Science Festival, and assisted them in creating bracelets which used beads to represent their birthdays and initials in binary.}
	\end{itemize}


\subsection*{Women and Identity in Gaming Symposium Invited Panelist}
     Lawrence University - 2015
\begin{itemize}
		\item{Discussed the research around women's identity in game development and other technology fields.}
	\end{itemize}

\subsection*{Woman's Hackathon Coordinator}
     University of Wisconsin-Madison - 2014
\begin{itemize}
		\item{Co-organized the 2014 International Woman's Hackathon at UW-Madison, including event planning, recruiting judges and mentors, soliciting donations, graphic design, and advertising.}
	\end{itemize}

\subsection*{Games Learning Society 2014 Conference Awards Designer}
     Learning Games Network - 2014
\begin{itemize}
		\item{Designed and created the Showcase awards for the GLS 2014 conference. The 4 award sizes were designed in 3D Lego modeling software, then the 2,000 custom selected LEGOs were purchased from 10 different international vendors to conform to budget and schedule constraints. A team of volunteers was guided in assembling the awards.}
	\end{itemize}

	\subsection*{Women's Designathon Organizer}{Doyenne Group}
     Madison, WI - 2013
	\begin{itemize}
		\item{Led organization and vision setting for this hackathon style 2-day event, including participating in fund-raising, mentor recruitment, advertising, graphic design, and participant recruitment.}
	\end{itemize}


	\subsection*{Volunteer Coordinator of Educational Technology}{Sector67}
     Madison, WI - 2012
	\begin{itemize}
		\item{Organized and taught courses on technology topics, including Linux, Java, and Technology for Students.}
	\end{itemize}

	\subsection*{Database Design Volunteer}{Grassroots Leadership College}
     Madison, WI - 2010--2012
	\begin{itemize}
		\item{Re-designed FileMaker databases for conversion to CiviCRM; recovered data with Pentaho.}
		\item{Led a committee of IT volunteers in setting a new IT vision.}
		\item{Troubleshot general office technology issues and provided various tech trainings.}
	\end{itemize}

\end{document}
