\documentclass[../main.tex]{subfiles}

\begin{document}

	\subsection*{Teaching Assistant}
     University of Wisconsin - Madison, Madison, WI - 2016--2017
	\begin{itemize}
		\item{Planned and led 75 minute classes on 'Video Games and Learning'.}
		\item{Advise 40 students a semester on successful writing strategies.}
		\item{Utilize Canvas and Desire to Learn to provide instructional support for students.}
	\end{itemize}

	\subsection*{Technology Trainer}
     Freelance, Madison, WI - 2016--2017
	\begin{itemize}
		\item{Designed custom curriculum on Google suite for a non-profit.}
	\end{itemize}


	\subsection*{Microsoft Student Partner}
     Microsoft, Madison, WI - 2016--2017
	\begin{itemize}
		\item{Organize monthly technical workshops for UW Madison students on a variety of topics, including games, mobile technology, web development, IoT Hardware and machine learning.}
	\end{itemize}

	\subsection*{Computer Science Tutor}
     University of Wisconsin - Madison, Madison, WI - 2016--present
	\begin{itemize}
		\item{Assist students in introductory computer science classes with code and theoretical concepts.}
	\end{itemize}

	\subsection*{Computer Science Workshop Designer}
     University of Wisconsin - Madison, Madison, WI - 2016--2017
	\begin{itemize}
		\item{Collaborating with a team to design and lead a MIT App Inventor workshop for freshmen who have not yet declared their major but are considering computer science.}
	\end{itemize}


	\subsection*{Adjunct Instructor of Information Technology}
     ITT Technical Institute, Madison, WI - 2011
	\begin{itemize}
		\item{Taught Linux System Administration, Windows 7, and Introduction to the PC (hardware tech support).}
	\end{itemize}

	\subsection*{Program Chair of Information Technology}
     Globe University East, Madison, WI - 2010--2011
	\begin{itemize}
		\item{Taught a variety of IT courses, including Operating Systems, Microsoft Office, Keyboarding, and Introduction to Computer Literacy.}
		\item{Provided programmatic support for students and faculty with training, advising, recruitment, and hiring.}
		\item{Developed and maintained facility and curriculum resources, including a Blackboard implementation.}
		\item{Organized and led community workshops.}
	\end{itemize}


	\subsection*{Peace Corps Information and Communication Technology (ICT) Teacher Volunteer}
     Peace Corps Ghana, Nalerigu, Ghana; Mampong, Ghana - 2007--2010
	\begin{itemize}
		\item{Creatively used limited resources to teach hands-on skills and theory to over 850 high school students, 200 elementary students, and 220 adults. Class sizes ranged from 4 to 70 students.}
		\item{Set up, administered and designed curriculum for one of the first networked dual boot Ubuntu Linux/Windows XP labs in Ghana. }
		\item{Mentored 5 high-school and university teachers with lesson planning and instructional design. }
		\item{Trained dozens of academic staff members in basic computer skills, hardware repair, software installations, and lab administration.}
		\item{Coordinated and produced student cultural dance and HIV/AIDS educational video projects.}
		\item{Helped organize the website, served as a group leader, and taught ICT at 3 annual week-long STARS (Students Taking Action Reaching For Success) high-school conferences.}
		\item{Created, promoted and distributed the ICT Resource CD for ICT teachers and students, which contained a full range of culturally appropriate instructional materials including lesson plans, exams, textbooks, educational open source software, and classroom technology tips.}
		\item{Coordinated the ICT Think-Tank: representing over 140 volunteers, this committee worked on dozens of cutting-edge technology projects, including designing and creating informational websites, writing educational computer lab manuals, and developing the Library Linux operating system. }
		\item{Organized and led the ICT technical training for incoming volunteers at numerous workshops and conferences.}
		\item{Organized and led four clubs (Staff Ubuntu Linux Club, Elective ICT Club, Websites and Internet Club, and the Middle School Girls Club) and coordinated projects with an HIV/AIDS club. }
	\end{itemize}

	\subsection*{ESL Computer Tutor Volunteer}
     Minnesota Literacy Council, Minneapolis, MN - 2006--2007
	\begin{itemize}
		\item{Tutored ESL adults in basic computer skills.}
	\end{itemize}

\end{document}
